Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-15 manuscript.tex
Correctly reference table [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/d0fe50ee2f2a7caa83758cf8364e3629637ef31a.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/d0fe50ee2f2a7caa83758cf8364e3629637ef31a/checks
https://github.com/habi/acinar-analysis-manuscript/runs/420944898

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/d0fe50ee2f2a7caa83758cf8364e3629637ef31a/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/d0fe50ee2f2a7caa83758cf8364e3629637ef31a}{habi/acinar-analysis-manuscript@d0fe50e}
on December 14, 2020.

@@

\leavevmode\hypertarget{ref-199ALtdJt}{}%
53. Replacement, Reduction, Refinement {[}Online{]}. \emph{ALTEX} 19: 73--78, 2002. \url{https://www.altex.org/index.php/altex/article/view/1106} {[}14 Dec. 2020{]}.
\end{cslreferences}

>>>>

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/d0fe50ee2f2a7caa83758cf8364e3629637ef31a/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/d0fe50ee2f2a7caa83758cf8364e3629637ef31a}{habi/acinar-analysis-manuscript@d0fe50e}
on December 15, 2020.

@@

\leavevmode\hypertarget{ref-199ALtdJt}{}%
53. Replacement, Reduction, Refinement {[}Online{]}. \emph{ALTEX} 19: 73--78, 2002. \url{https://www.altex.org/index.php/altex/article/view/1106} {[}15 Dec. 2020{]}.
\end{cslreferences}
